Methods for Large Scale Learning to Rank

### 2014-04-08 report/Chapters/CrossBenchmarkComparison.tex
plots ge-exporteerd, ge-annoteerd en ge-integreerd
TODO gevinkt: uitleg gebruikte metrics

@@

\section{Results \& Discussion}
\subsection{MAP}

\subsection{NDCG@3}

\subsection{NDCG@5}

\subsection{NDCG@10}

\subsection{All metrics}
Figure \ref{fig:normalised_winning_number_all} shows the normalised winning number as function of ideal winning number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum} and Table \ref{tab:raw_data_norm_winnum_cntd} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
%TODO: waarom ndcg@3,5,10 en MAP?
%TODO: limitations van deze vergelijkingsmethodologie

\section{Limitations}

>>>>

\acs{nDCG}@3, \acs{nDCG}@5, \acs{nDCG}@10 and \acs{MAP} are chosen as metrics on which the meta-analysis will be performed. These metrics seem to be the most frequently used evaluation metrics in most of the benchmark datasets used. An exception are the Yahoo! Learning to Rank Challenge datasets on which mainly \ac{ERR} is used as main evaluation metric. The lack of use of \ac{ERR} in other benchmarks makes it unsuitable for a cross-benchmark comparison.

@@

\section{Results \& Discussion}
\subsection{MAP}
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/map_winnum}
\caption{\acs{MAP} comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_map}
\end{figure}

\subsection{NDCG@3}
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/ndcg3_winnum}
\caption{\acs{nDCG}@3 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure}

\subsection{NDCG@5}
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/ndcg5_winnum}
\caption{\acs{nDCG}@5 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure}

\subsection{NDCG@10}
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/ndcg10_winnum}
\caption{\acs{nDCG}@10 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure}

\subsection{All metrics}
Figure \ref{fig:normalised_winning_number_all} shows the normalised winning number as function of ideal winning number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum} and Table \ref{tab:raw_data_norm_winnum_cntd} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.
\begin{figure}[!h]
\includegraphics[scale=0.35]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure}
